03 Data Vizualization

### 2022-06-08 03_data_viz.Rmd
updated save output

# Define a function for turnover plots
plot_turnover <- function(df, terrain_choice, color_choice) {
  df %>% 
  # Data organization and cleanup
  ungroup() %>% 
  filter(
    inc_time_d == "7",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra"
  )) %>% 
  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
  mutate(type = "unweighted") %>% 
  bind_rows(
    turnover_weighted_cleaned) %>%
  group_by(terrain) %>%

@@

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = compound,
      color = type,
      fill = type
      )
  ) +
  geom_point(size = 2) +
  geom_errorbar(aes(
    xmin = u_d_mc - (0.5 * su_d_mc),
    xmax = u_d_mc + (0.5 * su_d_mc)),
    width = 0,
    size = 1.1
    ) +
  coord_cartesian(xlim = c(0, 0.175)) +
  scale_fill_manual(values = c("black", color_choice)) +
  scale_color_manual(values = c("black", color_choice)) +
  scale_x_discrete(labels =)
  theme_classic() +
  labs(x = TeX("Turnover ($day^{-1}$)"),
       title = terrain_choice) +
  theme(
    axis.title.y = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.y = element_blank(),
    strip.background = element_blank(),
    legend.position = "none",
    plot.title = element_text(hjust = 0.5),
    panel.grid.major.x = element_line(linetype = "dotted")
  )

@@

cowplot::save_plot(
  filename = "fig_output/turnover_plot.pdf",
  plot = p_turnover,
  base_width = 11,
  base_height = 4
  )

>>>>

# Define a function for turnover plots
plot_turnover <- function(df, terrain_choice, color_choice) {
  df %>% 
  # Data organization and cleanup
  ungroup() %>% 
  filter(
    inc_time_d == "7",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "i-16:0")) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tundra")
    ) %>% 
  # mutate(
  #   compound = str_replace(
  #     string = compound, 
  #     pattern = "ω", 
  #     replacement = "$\omega$")
  # ) %>% 
  select(terrain, compound, inc_time_d, u_d, u_d_mc, gen_d, gen_d_mc, su_d, su_d_mc) %>%
  mutate(type = "unweighted") %>% 
  bind_rows(
    turnover_weighted_cleaned) %>%
  group_by(terrain) %>%

@@

  # Plot it
  ggplot(
    aes(
      x = u_d_mc,
      y = TeX(compound),
      color = type,
      fill = type,
      label = round(gen_d_mc, 1)
      )
  ) +
    geom_point(size = 2) +
    geom_errorbar(aes(
      xmin = u_d_mc - (0.5 * su_d_mc),
      xmax = u_d_mc + (0.5 * su_d_mc)),
      width = 0,
      size = 1.1
      ) +
    # Uncomment to show generation times
    # geom_text(
    #   nudge_x = 0.05
    # ) +
    coord_cartesian(xlim = c(0, 0.175)) +
    scale_fill_manual(values = c("black", color_choice)) +
    scale_color_manual(values = c("black", color_choice)) +
    theme_classic() +
    labs(x = TeX("Turnover ($day^{-1}$)"),
         title = terrain_choice) +
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),
      axis.ticks.y = element_blank(),
      strip.background = element_blank(),
      legend.position = "none",
      plot.title = element_text(hjust = 0.5),
      panel.grid.major.x = element_line(linetype = "dotted")
    )

@@

# ggsave(
#   plot = p_turnover,
#   filename = "fig_output/turnover_plot.pdf",
#   device = cairo_pdf, # Need this for greek symbols to render correctly
#   width = 11,
#   height = 4
#   )
